\cvsection{Experience}
\begin{cventries}

  \cventry
    {Full Stack Developer <Co-Founder>}
    {Tega}
    {Kigali, Angular \& Python}
    {Sept. 2022 --- Present}
    {
      \begin{cvitems}
        \item {Designed components, higher order components and reusable utilities in Angular.}
        \item {Developed and led the backend for the project using Django Rest Framework. }
        \item {Managed infrastructure and application security.}
        \item {Created mature, unambiguous coding standards for a team of 3 devs that improved consistency and maintainability across different code repositories.}
      \end{cvitems}
    }
  \cventry
    {Software Developer <Python Developer>}
    {PAC-LAB HITMS}
    {Cameroon --- Remote, Python \& Vanilla JS}
    {July. 2022 --- Present}
    {
      \begin{cvitems}
        \item {Deploy and maintain internal applications on Google App-engine on a daily basis.}
        \item {Developed Student Portal for Easy access to marks, courses and invoices in Django.}
        \item {Authored a functional Student Application system in Python/Django.}
        \item {Authored a custom admin portal for easy management of student information in Python/Django.}
        \item {Currently developing a Learning management system in Angular and Django.}
        \item {Optimizing Django Queries resulting in minimization of the average django server response time by 64\%. }
        \item {Connected multiple Django projects to share the same database, leading to high consistency across the system}
      \end{cvitems}
    }
  \cventry
    {Data Engineer <Python Developer>}
    {Imperial College London}
    {London --- Remote, Python}
    {Sept. 2021 --- Sept. 2022}
    {
      \begin{cvitems}
        \item {Extracted and ingested data from 78 websites using beautiful soup(BS4) and scrapy crawler.}
        \item {Developed custom spiderbots to perform complex google search operations.}
        \item {Compiled and Structured large datasets into Hdf5 format.}
        \item {Developed tools to ease downloading of videos and PDFs.}
        \item {Automated the compilation of data into multiple formats.}
        \item {Performed several root cause analysis on processes to improve performance of tools.}
      \end{cvitems}
    }
  \cventry
    {Software Developer <Site Reliability Engineer>}
    {BB Incubator}
    {Cameroon --- Remote, Python \& Vanilla JS}
    {March. 2021 --- Aug. 2022}
    {
      \begin{cvitems}
        \item {Fixed cases related to support escalation, improving site stability.}
        \item {Worked with mentees to setup online profiles.}
        \item {Authored BBIncubator website with an Application system for new mentees.}
        \item {Responsible for site availability, latency, performance, change management and emergency response.}
        \item {Developed data collection policies which served as a decision-taking tool for executive management.}
        \item {Integrated google analytics and microsoft clarity, increasing advertisement efficiency.}
        \item {Designed and modeled database tables and relations with PostgreSQL.}
      \end{cvitems}
    }
  \cventry
    {Software Developer <Python Developer>}
    {Befa language}
    {Kigali --- Part-time, Typescript \& Python}
    {Nov. 2019 --- Jan. 2022}
    {
      \begin{cvitems}
        \item {Performed research to explore and identify new technological platforms.}
        \item {Authored and secured APIs development using OAuth and JWT.}
        \item {Developed a Customer Relationship management app using  Python/Django.}
        \item {Contributed to mobile app using Flutter and Python/Django which improved user experience and response times.}
        \item {Developed a learning management app using Angular and Django Rest Framework.}
        \item {Designed and modeled database tables and relations with PostgreSQL.}
      \end{cvitems}
    }
  \cventry
    {Lead Facilitator <DSC Lead>}
    {Google Developer Students Club, KIM University}
    {Kigali --- full-time, Python, C++, \& JavaScript}
    {Sept. 2019 --- Sept. 2020}
    {
      \begin{cvitems}
        \item{Mobilized students and faculty to pioneer the first tech club with a permanent practice Lab.}
        \item {Collaborated with HOD to host 6 weeks Arduino and python bootcamp, significantly increasing overall interest in programming and IOT within the community.}
        \item {Helped increase women participation rates in weekly meetups through effective sensitization.}
        \item {Organized weekly meetups to teach Web technologies (HTML, CSS, JavaScript) and mobile application development (Java for Android).}
      \end{cvitems}
    }
  \cventry
    {Consultant <IT Administrator>}
    {Rise to Shine Company}
    {Kigali, Part-time}
    {Oct. 2018 --- Present}
    {
      \begin{cvitems}
        \item {Continuously trained new IT staff to manage and maintain IT Equipments.}
        \item {Identified, Repaired and maintained damaged computer parts.}
        \item {Ensured internet connectivity is operating at acceptable bandwidths.}
        \item {Created user accounts and performed access control.}
        \item {Performed diagnostic tests and debugging procedures to optimize computer systems.}
        \item {Helped in the procurement of \$7000 worth of laptops.}
        \item {Upgraded, installed and configured new hardware and software to meet company objectives.}
      \end{cvitems}
    }
  \end{cventries}
